---
title: "Scopus Biblio Search"
author: "Leonardo A. Saravia"
date: "8/27/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

require(litsearchr)
library(tidyverse)

theme_set(theme_bw())

```

# New SCOPUS search string

ALL ( ( microarthropods  OR  springtails  OR  mites  OR  oribatida  OR  mesostigmata  OR  prostigmata  OR  astigmata )  AND  ( trophic  OR  diet  OR  feeding )  AND  soil  AND  ( "gut content"  OR  "stable isotope"  OR  "food preference"  OR  "fatty acid"  OR  lipids  OR  metabarcoding )  AND  ( family  OR  genus  OR  species ) )  AND  ( LIMIT-TO ( SUBJAREA ,  "AGRI" )  OR  LIMIT-TO ( SUBJAREA ,  "ENVI" )  OR  LIMIT-TO ( SUBJAREA ,  "MULT" )  OR  LIMIT-TO ( SUBJAREA ,  "EART" ) )  AND  ( LIMIT-TO ( EXACTKEYWORD ,  "Collembola" )  OR  LIMIT-TO ( EXACTKEYWORD ,  "Acari" )  OR  LIMIT-TO ( EXACTKEYWORD ,  "Soil Fauna" ) )  AND  ( LIMIT-TO ( LANGUAGE ,  "English" )  OR  LIMIT-TO ( LANGUAGE ,  "Spanish" ) ) 


* Check if all previous articles are inside this new search

```{r biblio_check}


naiveimport <-
  litsearchr::import_results(directory = "Data", verbose = TRUE)

# Remove duplicates

naiveresults <-
  litsearchr::remove_duplicates(naiveimport, field = "title", method = "string_osa")

dups0 <- find_duplicates(naiveimport$title,method = "string_osa")


require(readxl)
require(synthesisr)
old_bib <- read_excel("Supplementary material I.xlsx")
names(old_bib)

titles <- c(old_bib$Title,naiveresults$title)
dups <- find_duplicates(titles,method = "string_osa")

#
# 
#




```

